Towards Patient-Specific Neural Field Modeling using Micro-Electrode Data

### 2011-05-11 ltx/data_paper/DataPaper.tex
edits to Result section

The estimated supports were then applied in the EM algorithm described in Section \ref{sec:EstimationAlgorithm} to estimate the smoothed states $\hat{\mathbf x}_t^b$, the connectivity kernel weights $\boldsymbol\theta$, the synaptic dynamic $\xi$, and the hyperparameters $\sigma_{\epsilon}^2$ and $\sigma^2_d$. A $5 \times 5$ square grid of basis functions with $2.25~mm$ spacing were used to cover the estimated support where $\sigma_{\psi}^2=3.5$. This is shown in Figure.\ref{fig:KernelWidthEstimation} by blue circles, each of which representing full width at half maximum of the connectivity kernel basis functions. The true and estimated connectivity kernel over 100 realisations are shown in Figure~\ref{fig:KernelEstimates}. Cross-sections of the estimates for each run are shown in Figure~\ref{fig:KernelEstimateCrossSection}. The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval. The large standard deviation is due to the high number of parameters need to be estimated.

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelBasis1.pdf}
\end{center}
\caption{{\bf Connectivity kernel basis functions, $n_{\theta}=25$}, $\sigma^2_{\theta}=3.5$.}
\label{fig:KernelWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
\end{center}
\caption{{\bf Disturbance support estimation}.}
\label{fig:DisturbanceWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimate.pdf}
\end{center}
\caption{{\bf Connectivity kernel estimates over 100 realisations.} left: True kernel; right;Estimated kernel.}
\label{fig:KernelEstimates}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimateCrossSection.pdf}
\end{center}
\caption{{\bf Cross-section of connectivity kernel estimates over 100 realisation.} True is blue; Estimate is green; 95\% Confedence interval is red.}
\label{fig:KernelEstimateCrossSection}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/Histogram.pdf}
\end{center}
\caption{{\bf Synaptic dynamic parameter and hyperparameter estimates}.}
\label{fig:Histogram}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/Q.pdf}
\end{center}
\caption{{\bf Lower-bound of the log-likelihood}. $Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$.}
\label{fig:FieldObserations}
\end{figure}

>>>>

The estimated supports were then applied in the EM algorithm described in Section \ref{sec:EstimationAlgorithm} to estimate the smoothed states $\hat{\mathbf x}_t^b$, the connectivity kernel weights $\boldsymbol\theta$, the synaptic dynamic $\xi$, and the hyperparameters $\sigma_{\epsilon}^2$ and $\sigma^2_d$. A $5 \times 5$ square grid of basis functions with $2.25~mm$ spacing were used to cover the estimated support where $\sigma_{\psi}^2=3.5$. This is shown in Figure.\ref{fig:KernelWidthEstimation} by blue circles, each of which representing full width at half maximum of the connectivity kernel basis functions. The true and estimated connectivity kernel for 100 Monte Carlo simulations are shown in Figure~\ref{fig:KernelEstimates}. Cross-sections of the connectivity kernel estimates for each run are shown in Figure~\ref{fig:KernelEstimateCrossSection}. The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel is inside the confidence interval. The large standard deviation is due to the high number of parameters need to be estimated. Figure~\ref{fig:Histogram} depicts the histogram of parameter estimates from 100 simulations where the true parameter value is shown by the solid line and the mean parameter estimate is shown by the dashed line. These histograms indicate small bias in parameter estimates with a very small standard deviation.

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelBasis1.pdf}
\end{center}
\caption{{\bf Connectivity kernel basis functions, $n_{\theta}=25$}, $\sigma^2_{\theta}=3.5$.}
\label{fig:KernelWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
\end{center}
\caption{{\bf Disturbance support estimation}.}
\label{fig:DisturbanceWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimate.pdf}
\end{center}
\caption{{\bf Connectivity kernel estimates over 100 realisations.} left: True kernel; right;Estimated kernel.}
\label{fig:KernelEstimates}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimateCrossSection.pdf}
\end{center}
\caption{{\bf Cross-section of connectivity kernel estimates over 100 realisation.} True is blue; Estimate is green; 95\% Confedence interval is red.}
\label{fig:KernelEstimateCrossSection}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/Histogram.pdf}
\end{center}
\caption{{\bf Synaptic dynamic parameter and hyperparameter estimates}.}
\label{fig:Histogram}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/Q.pdf}
\end{center}
\caption{{\bf Lower-bound of the log-likelihood}. $Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$.}
\label{fig:FieldObserations}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@
